SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-13 docs/questioning.tex
added an observation concerning Security
some fixes in the Conclusions section

@@

Despite many approaches that have been developed,
application attacks based on source code injection
have been consistently present for the last 15 years,
and it appears that they will continue to be.
Attackers seem to find new ways to introduce
source code to applications by using a variety of
languages and techniques~\cite{HNSHS12,DKH14}.
Meanwhile, during the last decade, there are
numerous mechanisms that have been developed to
detect one or more of such attacks. However,
even if some of them share characteristics
(for instance, {\sc html} sanitization and {\tt eval} handling)
with supported frameworks like Mozilla's Content Security
Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
({\sc csp}) and Google
Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06}
the majority of them are not used in practice.

In our research we tried to identify some of the reasons
why this is the case. Some of these reasons include
poor testing, high overhead, code unavailability,
deployment and security issues. However, our
systematization suggests that there are many
promising cases. For instance there are
mechanisms that have been extensively
tested in terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
{\sc dsi}, libAnomaly), solve specific
problems in an efficient way (Blueprint and the system
by Stock et al.) or have a low computational overhead
({\sc dsi} and the system by Phung et al.).
There are also cases that researchers have made their
code available ({\sc beep} and {\sc sd}river) which
can be a push towards the development of better
mechanisms. This argument has been raised
by another {\sc s}o{\sc k} paper too~\cite{SPWS13}.
We believe that testing defenses in
a production setting could also propel their adoption.

>>>>

An interesting observation is that mimicry attacks can be
used to bypass mechanisms coming from the hybrid category and
the policy enforcement and training subcategories.

@@

Despite many approaches that have been developed,
application attacks based on source code injection
have been consistently present for the last 15 years,
and it appears that they will continue to be.
Attackers seem to find new ways to introduce
malicious source code to applications by using a
variety of languages and techniques~\cite{HNSHS12,DKH14}.
Meanwhile, during the last decade, there are
numerous mechanisms that have been developed to
detect one or more of such attacks. However,
even if some of them share characteristics
(for instance, {\sc html} sanitization and {\tt eval} handling)
with supported frameworks like Mozilla's Content Security
Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
({\sc csp}) and Google
Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06}
the majority of them are not used in practice.

In our research we tried to identify some of the reasons
why this is the case. Some of these reasons include
poor testing, high overhead, code unavailability,
deployment and security issues. However, our
systematization suggests that there are many
promising cases. For instance there are
mechanisms that have been extensively
tested in terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
{\sc dsi}, libAnomaly), solve specific
problems in an efficient way (Blueprint and the system
by Stock et al.) or have a low computational overhead
({\sc dsi} and the system by Phung et al.).
There are also cases where researchers have made their
code available ({\sc beep} and {\sc sd}river) which
can be a push towards the development of better
mechanisms. This argument has been raised
by another {\sc s}o{\sc k} paper too~\cite{SPWS13}.
Finally, we believe that testing defenses in
a production setting could also propel their adoption.
